### 2015-09-09 prelim.tex
Cleaning up.

\section{Preliminaries}
\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as 
$$ \chi_M(\vect{x}) :=
	\begin{cases}
		1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
		\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface} \\
		0, & \text{if }\vect{x}\text{ is exterior to } M
	\end{cases}. 
$$.
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.

Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
\begin{eqnarray}
	\vec{V}(\vx) & := & \sum_{(\vect{s},\vect{n}) \in P}\left|\patch_s\right|F(\vx-\vect{s})\cdot\vn \label{eq:vdef} \\
	 & \approx & \sum_{(\vect{s},\vect{n}) \in P} \int_{\patch_s}{F(\vect{x} - \vect{p}) \nabla \chi (\vect{p})} \mathrm{d} \vect{p}. \notag  
\end{eqnarray}}
Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor. We return to this in \SC{sec:levelset}. The choice of $F$ places computational constraints on the resulting algorithm.

@@

Ideally, the filter $F$ should correspond to some globally supported RBF. However, as the support of $F$ grows, so does the cost of evaluating it at lattice sites. Moreover, the added benefit of a globally supported RBF is partially lost as the subsequent steps are entirely lattice-based and do not take the RBF into consideration. Our approach circumvents the choice of $F$ entirely by posing the gradient approximation problem as a variational problem that, in addition to imposing the interpolation constraint, also imposes constraints on the ``compactness'' and ``smoothness'' of the gradient approximation. The only kernel we need to consider is the one that generates our target shift-invariant space, i.e. the space used to recover the smoothed indicator function. This type of variational reconstruction can be seen as an approximation to radial basis approaches~\cite{variational}, and is well-suited to our Poisson formulation in shift-invariant spaces.

@@

\subsection{Sampling Lattices} \label{sec:smpl_review}
In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis. However, when sampling multivariate signals the situation is not as straightforward. A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling). If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\vect{n} : \vect{n} \in \intn^3 \}$ represents all possible sampling lattices. $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$. The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$. Finally, to control the sampling rate of a function a uniform scaling parameter $h$ is introduced -- lattices scaled by this parameter will be denoted by $\lattice{L}_h$. Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space, or even about the surface of the model, but the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).

@@

The Body-Centered Cubic (BCC) lattice is generated by the matrix  {\footnotesize
\begin{equation*} 
	\mathbf{L}_B := \frac{1}{\sqrt[3]{4}}
	\begin{bmatrix}
		-1 & 1 & 1 \\ 
		1 & -1 & 1 \\ 
		1 & 1 & -1 
	\end{bmatrix}.
\end{equation*}}
However, the BCC lattice is non-separable, and requires special care in data retrieval and indexing. \FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself.)

@@

\subsection{The Error Kernel}
The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
quantified via an error kernel in the Fourier domain. It is defined as
\begin{equation}
	E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
	+ 
	\underbrace{
	\ft{A}_{\varphi}(\vect{\omega})
	\abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
 		\ft{\dual{\varphi}}(\vect{\omega})}^2
  	}_{E_{\mathsf{res}}(\vect{\omega})}.
  \label{eq:scErrorKernel}
\end{equation}
For a bandlimited function $f$ whose spectrum is entirely contained
within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
\begin{equation}
	\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
	\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
	\label{eq:avgError}
\end{equation}
whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over all possible shifts of $f$. Even though this kernel was initially proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate non-Cartesian extensions have also appeared in the literature~\cite{condat05hexagonal, condat07, condat08, alim10, condat11}. Note that the minimum-error approximation scenario occurs when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$, or in other words $\analysis{\varphi}$ is chosen to be $\dual{\varphi}$.

\subsection{Approximation Error}

If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$. We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively. When this is the case, the minimum-error approximation is unattainable. However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\aspace{\lattice{L}_h}{\varphi}$, maintain the same order of accuracy.

For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order. Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.

@@

Finding $g$ that minimizes equation \EQ{eq:minexp} involves rewriting the minimization problem in terms of $\mathbf{c}$ \cite{xu2012rec}. Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$, $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$, and $P_{i,j} := \varphi_j(\vx_i)$ as before. Since $\varphi$ is known in closed form in our test cases, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically. The above vector equation can be solved using the Conjugate Gradient method.

>>>>

\section{Preliminaries}
\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as 
$$ \chi_M(\vect{x}) :=
	\begin{cases}
		1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
		\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface} \\
		0, & \text{if }\vect{x}\text{ is exterior to } M
	\end{cases}. 
$$
The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, (i.e, it approximates the smoothed gradient of the indicator function) finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. 
Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point. 
For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.

As in the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
\begin{eqnarray}
	\vec{V}(\vx) & := & \sum_{(\vect{s},\vect{n}) \in P}\left|\patch_s\right|F(\vx-\vect{s})\cdot\vn \label{eq:vdef} \\
	 & \approx & \sum_{(\vect{s},\vect{n}) \in P} \int_{\patch_s}{F(\vect{x} - \vect{p}) \nabla \chi (\vect{p})} \mathrm{d} \vect{p}. \notag  
\end{eqnarray}}
Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. 
We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor, we return to this in \SC{sec:levelset}. 
The choice of $F$ places computational constraints on the resulting algorithm.

@@

Ideally, the filter $F$ could correspond to some globally supported RBF. 
However, as the support of $F$ grows, so does the cost of evaluating it at lattice sites. 
Moreover, the added benefit of a globally supported RBF is partially lost as the subsequent steps are entirely lattice-based and do not take the RBF into consideration. 
Our approach circumvents the choice of $F$ entirely by posing the gradient approximation problem as a variational problem that, in addition to imposing the interpolation constraint, also imposes constraints on the ``compactness'' and ``smoothness'' of the gradient approximation. 
The only kernel we need to consider is the one that generates our target shift-invariant space, i.e. the space used to recover the smoothed indicator function. 
This type of variational reconstruction can be seen as an approximation to radial basis approaches~\cite{variational}, and is well-suited to our Poisson formulation in shift-invariant spaces.

@@

\subsection{Sampling Lattices} \label{sec:smpl_review}
In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis. 
However, when sampling multivariate signals the situation is not as straightforward. 
A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling). 
If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\vect{n} : \vect{n} \in \intn^3 \}$ represents all possible sampling lattices. 
$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we will assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$. 
The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$. Finally, to control the sampling rate of a function a uniform scaling parameter $h$ is introduced -- lattices scaled by this parameter will be denoted by $\lattice{L}_h$. 
Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space, or even about the surface of the model, but the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).

@@

The Body-Centered Cubic (BCC) lattice is generated by the matrix  {\footnotesize
\begin{equation*} 
	\mathbf{L}_B := \frac{1}{\sqrt[3]{4}}
	\begin{bmatrix}
		-1 & 1 & 1 \\ 
		1 & -1 & 1 \\ 
		1 & 1 & -1 
	\end{bmatrix}.
\end{equation*}}
However, the BCC lattice is non-separable, and requires special care in data retrieval and indexing. 
\FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself).

@@

\subsection{The Error Kernel}
The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation $\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be quantified via an error kernel in the Fourier domain. 
It is defined as
\begin{equation}
	E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
	+ 
	\underbrace{
	\ft{A}_{\varphi}(\vect{\omega})
	\abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
 		\ft{\dual{\varphi}}(\vect{\omega})}^2
  	}_{E_{\mathsf{res}}(\vect{\omega})}.
  \label{eq:scErrorKernel}
\end{equation}
For a band-limited function $f$ whose spectrum is entirely contained within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
\begin{equation}
	\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
	\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
	\label{eq:avgError}
\end{equation}
whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over all possible shifts of $f$. 
Even though this kernel was initially proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate non-Cartesian extensions have also appeared in the literature~\cite{condat05hexagonal, condat07, condat08, alim10, condat11}. 
Note that the minimum-error approximation scenario occurs when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$, or in other words $\analysis{\varphi}$ is chosen to be $\dual{\varphi}$.

\subsection{Approximation Error}
If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$. 
We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively. 
When this is the case, the minimum-error approximation is unattainable. 
However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\aspace{\lattice{L}_h}{\varphi}$, maintain the same order of accuracy.

For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order. 
Another nicety of these spaces is that data processing techniques -- derivative approximation for example -- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.

@@

Finding $g$ that minimizes equation \EQ{eq:minexp} involves rewriting the minimization problem in terms of $\mathbf{c}$ \cite{xu2012rec}. 
Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$, $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$, and $P_{i,j} := \varphi_j(\vx_i)$ as before. 
Since $\varphi$ is known in closed form in our test cases, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically. 
The above matrix equation can be solved using the Conjugate Gradient method.

### 2015-09-09 relatedwork.tex
Cleaning up.

\section{Related Work}
Surface reconstruction is still a very active area of research in computer graphics and it's beyond the scope of this work to touch on all the material related to the subject. We therefore very briefly review some relevant contributions -- those seeking a more in-depth review may look to a recent survey of the field \cite{reconstar_eg14}. We focus mainly on some of the more related and recent developments.

Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. They attempt to 
reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface. Other non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.

@@

One of the most well known implicit algorithms is the algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
tangent planes is constructed to create an approximation to a surface's distance function. A more recent work, is the Smoothed
Signed Distance Field reconstruction technique \cite{ssdrecon}, in which an oriented point set imposes constraints on the reconstructed function, its gradient, and its Hessian. These constraints are equvalent to requiring that the reconstructed function be an approximation to the distance field of the original model. Other techniques attempt to reconstruct a signed distance function within a function space spanned by radial basis functions \cite{radial}. Recently, there has also been research that incorporates point normals into the radial basis reconstruction framework \cite{hermite}. It's also possible to construct an implicit function as a normalize sum of compactly supported basis functions defined over an oct-tree, essentially ``smearing'' the point-set around space and constructing an indicator ``shell'' around them \cite{Fuhrmann2014}.

Another approach is to find an indicator function that approximates the ``inside-outside'' function of original model. An early technique \cite{fftk} transforms the smoothed gradient to the Fourier domain, applies an appropriate operator, then reconstructs it in the spatial domain. This approach often deals well with incomplete, missing, or otherwise noisy data and has the guarantee of creating a water tight surface. However, it involves reconstructing the indicator on a regular grid, which becomes very memory intensive as the grid is refined.

Poisson surface reconstruction techniques make the observation that the Fourier method is equivalently stated as a spatial Poisson problem \cite{Kazhdan06,screenedk}. Moreover, they seek to rectify the memory limitations of that work, while still maintaining its benefits. However, current techniques based on this idea have been shown to over-smooth the initial point-set, and therefore the resulting surface. \cite{reconbench}.

It is also possible to reconstruct the indicator of a point set within a wavelet basis \cite{wavelet}. In this work, an approximate indicator function of the model is projected onto a compact wavelet basis. This leads to a simple and efficient algorithm even when the data sets are massive. However the method's speed comes at a price, as the resulting surfaces are often non-smooth, and display many ``jagged'' artifacts (although a form of smoothing is applied to the resulting indicator function in an attempt to rectify this.)

@@

Our approach aims to solve the Poisson surface reconstruction problem in the setting of general shift-invariant spaces. A crucial step in this regard is the accurate estimation of the divergence of the gradient field from the oriented point-set. Radial basis functions (RBFs) are generally used in the context of the reconstruction of scattered data, however, RBF techniques are often computationally expensive, requiring the solution of large unstable systems of equations (for exact interpolation.) A proposed solution to this problem is to ``\emph{re-sample}'' the input data onto a regular shift-invariant space. This allows one to use efficient compact reconstruction kernels and data processing techniques \cite{variational,onvari}. Recently, an extension of this idea to box spline spaces \cite{xu2012rec} proposes a variational reconstruction framework in which the BCC lattice consistently outperforms the Cartesian lattice. Our method takes a similar variational approach and seeks to construct a smoothed lattice-based approximation of the gradient of the indicator function (\SC{sec:obtainingV}). Our employed constraints force the gradient to be close to zero away from the surface, while maintaining a certain degree of smoothness in the resulting approximation. This is preferable in comparison to other works \cite{fftk,Kazhdan06,screenedk} in which each sample is trilinearly distributed about either a grid or an oct-tree respectively, and is known to over-smooth data.

@@

Once, the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e. solving the Poisson system). To do this, we take an approach that is also inspired by filtering methodologies in signal processing. In particular, we're interested in an approximate solution to Poisson?s equation that lies in a chosen shift-invariant space. Our solution methodology is reminiscent of the finite element method. However, we do not impose any boundary conditions on the generating kernels. Rather, we satisfy homogeneous Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd (Section III). The solution is obtained by applying a digital filter to point samples. We approach the problem from first principles and derive the tools necessary to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).

>>>>

\section{Related Work}
Surface reconstruction is a very active area of research in computer graphics and it's beyond the scope of this work to touch on all the material related to the subject. We therefore very briefly review some relevant contributions -- those seeking a more in-depth review may look to a recent survey of the field \cite{reconstar_eg14}.
We focus mainly on some of the more recent and related work.

Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. 
They attempt to reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface. 
Non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.

@@

One of the most well known implicit algorithms is the algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
tangent planes is constructed to create an approximation to a surface's distance function. 
A more recent work, is the Smoothed Signed Distance Field reconstruction technique \cite{ssdrecon}, in which an oriented point set imposes constraints on the reconstructed function, its gradient, and its Hessian. 
These constraints are equivalent to requiring that the reconstructed function be an approximation to the distance field of the original model. 
Other techniques attempt to reconstruct a signed distance function within a function space spanned by radial basis functions \cite{radial}. 
Recently, there has also been work that incorporates point normals into a radial basis reconstruction framework \cite{hermite}. 
It's also possible to construct an implicit function as a normalize sum of compactly supported basis functions defined over an oct-tree, essentially ``smearing'' the point-set around space and constructing an indicator ``shell'' around them \cite{Fuhrmann2014}.

Another implicit approach is to find an indicator function that approximates the ``inside-outside'' (indicator) function of original model. 
An early technique \cite{fftk} transforms the smoothed gradient to the Fourier domain, applies an appropriate operator, then reconstructs it in the spatial domain. 
This approach often deals well with incomplete, missing, or otherwise noisy data and has the guarantee of creating a water tight surface. 
However, it involves reconstructing the indicator on a regular grid, which becomes very memory intensive as the grid is refined.

Building on that work, Poisson surface reconstruction techniques make the observation that the Fourier method is equivalently stated as a spatial Poisson problem \cite{Kazhdan06,screenedk}. 
Moreover, they seek to rectify the memory limitations of that work, while still maintaining its benefits. However, current techniques based on this idea have been shown to over-smooth the initial point-set, and therefore the resulting surface. \cite{reconbench}.

It is also possible to reconstruct the indicator of a point set within a wavelet basis \cite{wavelet}. 
In this work, an approximate indicator function of the model is projected onto a compact wavelet basis. 
This leads to a simple and efficient algorithm even when the data sets are massive. 
However the method's speed comes at a price, as the resulting surfaces are often non-smooth, and display many ``jagged'' artefacts (although a form of smoothing is applied to the resulting indicator function in an attempt to rectify this.)

@@

Our approach aims to solve the Poisson surface reconstruction problem in the setting of general shift-invariant spaces. 
A crucial step in this regard is the accurate estimation of the divergence of the gradient field from the oriented point-set. Radial basis functions (RBFs) are generally used in the context of the reconstruction of scattered data, however, RBF techniques are often computationally expensive, requiring the solution of large unstable systems of equations (for exact interpolation). 
A proposed solution to this problem is to ``\emph{re-sample}'' the input data onto a regular shift-invariant space. 
This allows one to use efficient compact reconstruction kernels and data processing techniques \cite{variational,onvari}. 
Recently, an extension of this idea to box spline spaces \cite{xu2012rec} proposes a variational reconstruction framework in which the BCC lattice consistently outperforms the Cartesian lattice. 
Our method takes a similar variational approach and seeks to construct a smoothed lattice-based approximation of the gradient of the indicator function (\SC{sec:obtainingV}). 
Our employed constraints force the gradient to be close to zero away from the surface, while maintaining a certain degree of smoothness in the resulting approximation. 
This is preferable in comparison to other works \cite{fftk,Kazhdan06,screenedk} in which each sample is trilinearly distributed about either a grid or an oct-tree respectively, and is known to over-smooth data.

@@

Once the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e. solving the Poisson system). 
To do this, we take an approach that is also inspired by filtering methodologies in signal processing. In particular, we're interested in an approximate solution to Poisson?s equation that lies in a chosen shift-invariant space. 
Our solution methodology is reminiscent of the finite element method. However, we do not impose any boundary conditions on the generating kernels. Rather, we satisfy homogeneous Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd (Section III). 
The solution is obtained by applying a digital filter to point samples. We approach the problem from first principles and derive the tools necessary to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).
